|

### 2020-09-22 paper.Rmd
reworking discussion

In this paper we have introduced the sage display, a visualisation technique for reversing
the curse of dimensionality in low dimensional projections of high dimensional data, and have shown its utility in applications in the natural sciences and machine learning. 
The new method combines animated linear dimension reduction obtained with a grand tour and a non-linear transformation of the projected data points to improve intelligibility of each view.
Our case studies show how it reduces the effects of data piling and aids different tasks in exploratory high dimensional data analysis.

The approach  provides interpretable visualisation that captures high dimensional information and preserves global structure, and it is complementary to non-linear dimension reduction techniques. For example, when visualising clusters, the sage display enables an assessment of cluster sizes, and accurately captures relative position and orientation. However, the sage display is currently 
naive to information in high dimensional space that is not 
captured by linear projections. Like t-SNE, it would be interesting to explore
transformations of projections where points in the high dimensional space are 
locally dense instead of expanding from the center of the distribution.

XXX option to reference upcoming work in liminal paper when mentioning complementarity

While the recently introduced slice tour [@sliceTour] is essentially addressing the same issue as the sage display (i.e. overplotting of points from the orthogonal space), it follows a different philosophy: we only select a small portion of the volume for plotting, based on the orthogonal distance of points from the projection plane. This approach is preferred for large sample sizes, or for concave structure, while the sage display works better in the case of limited sample size.

The sage display is easily incorporated into exploratory high dimensional data analysis, and applications shown in Section \ref{sec:application} provide examples of the following tasks:

@@

The applications also show that tuning is often required,
especially if the projection is dense in the center of the 
distribution. Expanding around the center aggressively can introduce distortions
in the display, a well known problem from non-linear dimension reduction techniques like t-SNE.
However, unlike those methods, the parameters in the sage display are 
interpretable; we know the effect of altering $\gamma$ and $R$ on the resulting 
visualisation. Recall that the radial transformation is approximately linear near
the center, thus preserving structures such as those seen in the pdfsense and
pollen applications. On the other hand, the tuning example showed how points away
from the projected center get moved to the edge of the hypersphere as $\gamma$
is increased or $R$ is decreased.

Given
that the display is quick to compute, being able to modify these parameters in 
real time with an interactive interface would be beneficial.

>>>>

This paper has introduced the sage tour, which reduces the data piling effects 
that occur when taking low dimensional projections of high dimensional data.
This new technique is easily incorporated into exploratory high dimensional data analysis, and applications shown in Section \ref{sec:application} provide examples of the following tasks:

@@

The approach  provides interpretable visualisation that captures high dimensional information and preserves global structure, and it is complementary to non-linear dimension reduction techniques. For example, when visualising clusters, the sage display enables an assessment of cluster shapes, and accurately captures relative position and orientation. The burning sage transformation is global and does not magnify local structure like t-SNE does.

However, the sage display is currently 
naive to information in high dimensional space that is not 
captured by linear projections. Like t-SNE, it would be interesting to explore
transformations of projections where points in the high dimensional space are 
locally dense instead of expanding from the center of the distribution.

An alternative is the slice tour [@sliceTour] which  allows distributions
of points around the center of the data to be explored using sections instead of projections. The slice tour is useful when there are large numbers of observations
or if there is concave structure in the data.

The sage tour can be tuned to more aggressively expand the center of the display. 
All of the examples shown had some tuning.  The last example 
demonstrated how points away from the projected center get moved to the edge of the hypersphere as $\gamma$ is increased or $R$ is decreased. The non-linear
transformation can introduce distortions which is a well known problem for any
non-linear dimension reduction technique including t-SNE. However, any distortion
introduced by the sage display are interpretable because it is controlled
by a simple function (equations xxx).

The sage display is fast to compute, which lends itself to being embedded into
an interactive interface. An ideal interface would allow real time changes to the
parameters of the transformation. This would be especially useful when coupled with linked brushing in complementary views.
